Constraint Programming - Inside Gecode

### 2014-05-03 paper.tex
corrections

	\subsubsection{Depth-First Search}
	The Depth-First Search is a good point to start, as it was also historical the first developed one. The idea behind this search algorithm is that every possible combination of variables is examined. Obviously in its basic form it can not be applied to problems with inifinite domains; for such problems with such variable domains it is necessary to use for example a Branch-and-Bound Search.

@@

	\subsubsection{Backtracking}

>>>>

	\subsubsection{Depth-First Search}
	The Depth-First Search is a good point to start, as it was also historical the first developed one. The idea behind this search algorithm is that every possible combination of variables is examined. Obviously in its basic form it can not be applied to problems with inifinite domains; for problems with such variable domains it is necessary to use for example a Branch-and-Bound Search.

@@
